Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes

### 2024-11-04 paper/paper.qmd
edits to paper

Kamala is predicted to win the remaining states and is given fairly high chances of locking these up. despite only winning Nevada, North Carolina and Pennsylvania by under a percentage point in the model Kamala's probability of winning those electoral votes is very high. This is due to the small standard deviations shown in @Tab-2 making the predicted outcome of a victory more secure.

@@

## 1. Sampling Approach

@@

## 2. Recruitment of Respondents

@@

## 3. Data Validation and Bias Reduction

@@

## 4. Poll Aggregation

@@

## 5. Budget Allocation

@@

## 6. Question Design and Goal Alignment
The goal of our survey is to predict who will win the election, this is the research question that guides our survey. In order to achieve this, our questions will isolate the relevant variables by asking only one thing at a time (ceteris paribus). We will also use item-specific scales over agree-disagree formats to avoid acquiescence bias. Furthermore, we will randomize response options in order to mitigate response order bias and emphasize the survey's anonymity to minimize social desirability bias.

>>>>

Kamala is predicted to win the remaining states and is given fairly high chances of locking these up. despite only winning Nevada, North Carolina and Pennsylvania by under a percentage point in the model Kamala's probability of winning those electoral votes is very high. This is due to the small standard deviations shown in @Fig-5 making the predicted outcome of a victory more secure.

@@

## Sampling Approach

@@

## Recruitment of Respondents

@@

## Data Validation and Bias Reduction

@@

## Poll Aggregation

@@

## Budget Allocation

@@

## Question Design and Goal Alignment
The goal of our survey is to predict who will win the election, this is the research question that guides our survey. In order to achieve this, our questions will isolate the relevant variables by asking only one thing at a time (ceteris paribus). We will also use item-specific scales over agree-disagree formats to avoid acquiescence bias. Furthermore, we will randomize response options in order to mitigate response order bias and emphasize the survey's anonymity to minimize social desirability bias.
